Bayesian statistics and swine flu

### 2009-08-12 docs/pandemic/bayesPandemic.rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@355 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\documentclass{beamer}
\usepackage[nogin]{Sweave}
\title{Bayesian statistics and  swine flu}
\author{Patrick Brown$^1$,  Peter Neal$^2$}
\institute{1:Cancer Care Ontario and Dalla Lana School of Public Health, University of Toronto; 2: University of Manchester} 
\usepackage{amsmath,subfigure}

@@

@@

@@

>>>>

\documentclass{beamer}
\usepackage[nogin]{Sweave}
\title{Bayesian statistics and  swine flu}
\author{Patrick Brown$^1$,  Peter Neal$^2$}
\institute{1:Cancer Care Ontario and Dalla Lana School of Public Health, University of Toronto; 2: School of Mathematics, University of Manchester} 
\usepackage{amsmath,subfigure}

@@

\begin{frame}
\frametitle{Severity of infection}

@@

\begin{frame}
\frametitle{The Algorithm}
data augmentation

random walk metropolis on parameters
\end{frame}

@@

\begin{frame}
\frametitle{Results}

\begin{frame}
\frametitle{Age?}

piecewise constant 5yr?

change points?

note that after data augmentation it's a standard problem.
